Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-05-06 fib2.tex
Slight rewording in third paragraph of intro. Added fault-tolerant decoders as an open problem.

Topologically ordered quantum systems in two dimensions offer tremendous promise for 
long-term storage and processing of quantum information~\cite{Kitaev2003, Dennis2002, Nayak2008}. 
The topological features of such systems are insensitive to local 
perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and have excitations 
displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
quantum computation~\cite{Freedman2002, Nayak2008}.

@@

Almost all of the sizable research effort on active quantum error correction for topological 
systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Andrist2015}.
%~\cite{Dennis2002, Duclos-Cianci2010, Bravyi2011, Bravyi2014}.
While decoding algorithms are generally designed to run efficiently, simulating the physical error correction procedure also requires simulating the dynamics of the noise and recovery processes. 
Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) these processes can be efficiently simulated numerically, allowing lattice 
simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
Standard algorithms are specifically tailored to exploit the abelian nature of these particles, and in particular the fact that abelian anyons cannot be used for quantum computation.

@@

There are several interesting avenues for further research. Although it is not completely obvious how to do so, applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems. Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.

>>>>

Topologically ordered quantum systems in two dimensions offer tremendous promise for 
long-term storage and processing of quantum information~\cite{Kitaev2003, Dennis2002, Nayak2008}. 
The topological features of such systems are insensitive to local 
perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations 
displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
quantum computation~\cite{Freedman2002, Nayak2008}.

@@

Decoding algorithms are generally designed to run efficiently, but simulating the physical error-correction procedure also requires simulating the dynamics of the noise and recovery processes. 
Because of this, almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
%~\cite{Dennis2002, Duclos-Cianci2010, Bravyi2011, Bravyi2014}.
Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) noise and recovery processes can be efficiently simulated numerically, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
Standard algorithms are specifically tailored to exploit the abelian nature of these particles, and specifically that abelian anyons cannot be used for quantum computation.

@@

There are several interesting avenues for further research. 
Although it is not completely obvious how to do so, applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems. 
Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
Finally, perhaps the most important open question is whether \emph{fault-tolerant} decoders can be designed for nonabelian anyon codes.
